Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-02 papers/B1555_EdgeOn/B1555_letter.tex
Rewrite on Discussion[complete version]

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. The discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe. Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites. This makes gravitational lensing a powerful tool for the detection of substructures. The gravitational perturbation from substructure is sufficient to bring flux ratio anomaly in strong lensing systems. These perturbations reflect the total mass of substructures. Give directly measurement of mass function and avoid assumptions on how baryonic matter distributes with dark matter.

The discussion on substructure searching in strong lensing systems are mostly done by multiple images of lensed quasar. Until now there are a dozen(?) flux anomalous lensed quasars and the number must increase in the future surveys. With the assumption of smooth gravitational potential from lens galaxy, flux ratio anomalies are brought by substructure perturbations. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomalies, including B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP K-band image, which an edge-on disk lies across between the positions of radio merging double A \& B. 
more complicated structure

In sec. 2, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to exist to cause the observed flux ratio anomaly. This indicates the flux ratio anomaly in B1555+375 is resulted from the structure of lens galaxy itself, which is the edge-on disk seen in the SHARP infrared imaging. Our result is consistent with the conclusion from \citet{Xu14}. Their simulation gives a low probability on the hypothesis that substructure causing flux anomaly in B1555+375.

With our discover in B155+375, we show that the lens galaxy structure can dominate the flux ratio anomalous phenomenon in strong lensing system. This leads to a more general reminder. Not all of the flux anomalies indicate the existence of substructures. One must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data and analysis. For the flux ratio anomalies caused by real dark matter substructures and dwarf galaxies, non-stucture effects would also influence the estimated mass and other derived properties. Thus, we would like to draw some attention on these non-substructure effects. Once we understand more about their role in flux anomalous phenomenon, we can be more confident on searching unseen dwarf galaxies and dark matter substructures by searching flux ratio anomalous systems.

Thus radio data provides reliable information for constraint and modelling because it avoids the problem of dust extinction and micro lensing from stars. On the other hand, optical or near infrared imaging also gives useful information about the lensing system. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The lack of knowledge about lens galaxy, e.g. modelling with radio data alnog, may lead to an improper lens model.
Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. The radio and narrow band observations are the best approaches to obtain accurate flux ratio data. However, optical and infrared imaging can provide more information on the structure of lens galaxy. With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\

>>>>

\section{Discussion}
The abundance of substructure within galaxy-size halo has been an undetermined problem in structure formation studies. Discrepency between numerical simulation and observation within the Local Universe gives two possible interpretations: an alternative structure formation model or small sample from the Local Universe. Difficulties emerge while searching beyond the Local Group due to the low luminosity of satellites. This makes gravitational lensing a powerful tool for the detection of substructures. With the fact that surface brightness is sensitive to gravitational perturbation, flux ratio anomaly in strong lensing system becomes a sign of existence of subhalo and also reflects its total mass. Give directly measurement of mass function which can avoid making assumptions on how baryonic matter distributes with dark matter.

Discussions on substructure searching in strong lensing system are mostly done by multiple images of lensed quasar. Until now there are a dozen(?) flux anomalous lensed quasars, and the number must increase in the future surveys. In the ideal case(no extinction and micro lensing), flux ratio anomalies are brought by substructure perturbations with the assumption that lens galaxy has smooth gravitational potential. Numerical simulations have examined this idea with known lensed quasars. In \citet{Xu14}, they found that substructure cannot expalin for all of radio flux anomalous phenomena. Only 1 out of 6 lens systems can be reproduced the flux anomaly by adding subhalos on to the system. The rest of them are only few percent likely to have substructure origined flux anomaly, including our target B1555+375. They conclude B1555+375 with improper lens model. This result can be supported by SHARP K-band image, which an edge-on disk lies across between the radio merging double A \& B. A more complicated lens model (e.g. include an exponential disk) must be applied on B1555+375.

In part 3, we present new lens models of B1555+375 with a bulge and an edge-on disk. Our models better match to the radio image positions than in \citet{Marlow} and also explain the flux ratio anomaly between components A and B. In our modelling, substructure is not neccessary to presence and a  exponential disk with high ellipcity well explains the observed flux ratio anomaly. This indicates that in B1555+375, flux ratio anomaly is caused by structure of lens galaxy itself rather than substructure. Our discover brings out a reminder: not all of flux ratio anomalies in lensed quasar indicate the existence of substructure even without the problem of dust extinction and micro lensing from stars. A complex host galaxy mass distribution can dominate flux ratio anomalous phenomenon in strong lensed quasar. Thus, one must fully consider non-substructure effects before gathering any statistics or serious analysis. Otherwise, these ``false'' substructures that detected by flux anomalies can serverly biased the data analysis. For the case oringinated by real  substructures, mass distribution of host galaxy may also influence the estimated mass and other derived properties. We would like to draw attention on this non-substructure effect in flux anomalous lensed quasar. Not untill non-substructure effects in flux ratio anomalous systems been understood, statistics from  lensed quasars may contain large systematic bias.

Our result also shows that multi-wavelength image is helpful on exploring flux ratio anomalous systems. Although radio data provides reliable information for constraint and modelling, optical and near-infrared imaging provides useful information about mass distribution of host galaxy. In the previous paper of SHARP, \citet{SHARP12} show that high resolution IR imaging improves the lens modelling. The improvement is even more dramatic in B1555+375 while adding an edge-on disk can well explain flux ratio anomaly. Lack of knowledge on lens galaxy surely leads to an improper lens model sometimes. With the first system being analyzed and shown that an edge-on disk can cause flux ratio anomaly, our follow up will be explore other SHARP systems. In Figure 3, all of these systems have a recognizable edge-on disk in infrared imaging. The flux ratio anomalies of these systems may also able to be explained by an edge-on disk structure.\\
